A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-05 manuscript.Rmd
some more on PR

The selected model parameters should express our expectations for the Machiavellism subscale of the short dark triad [SD3, @Jones2013].

As a starting point, we can use already published information.
@Jones2013 report a set of factor loadings from an Exploratory Structural Equation Model [@asparouhovExploratoryStructuralEquation2009].
The estimates for the construction sample, which was recruited from Amazon’s Mechanical Turk (MTurk) and consists of 489 adults from Canada and the United States, can be seen in Table \@ref(tab:loadings))
They report a gender difference (at the manifest level) depending on the study between `r min(cohend_jones_paulhus)` and `r max(cohend_jones_paulhus)`.

@@

@@

To verify the data integrity, you can include a line of code after reading the data that looks like this:
<!-- AP: shouldn't this be wrapped into a repro function and also stored in the YAML header??? -->

>>>>

The selected model parameters should express our expectations for the Machiavellism subscale of the short dark triad (SD3). <!-- AP: reference needed; explain the scale. What is the construct that we are measuring here? -->
As a starting point, we can use already published information.
@Jones2013 report a set of factor loadings (see Table \@ref(tab:loadings)) <!--AP what was the reference population? what was the sample size? --> and report a gender difference (at the manifest level) depending on the sample between `r min(cohend_jones_paulhus)` and `r max(cohend_jones_paulhus)`. <!--AP why not on the latent level? They report factor loadings after all? Please explain-->

@@

### GitHub Project Management

<!--Hands on: Introduce GitHub Projects-->
<!--I love it, but maybe we should remove it-->
While issues and pull requests already provide much structure to organize your work, GitHub projects allow you to categorize and prioritize issues and pull request, while informing you on the progress you made.

@@

To verify the data integrity you can include a line of code after reading the data that looks like this:
